Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-09 minimax.tex
More TODOs (yeah)
new figures and tables, more on rel work

\section{Related Work}
\label{sec:related}
In a social choice context, an increasing number of authors has been interested in obtaining information about winners with reduced assumptions about the knowledge of the agent preferences, assuming that the voting rule is known. \Citet{Conitzer2005} have studied the complexity of communication, using different voting rules, determining lower and upper bounds for it. They showed that, in the worst case, the agents should send their complete set of preference for most of the rules they investigated. \Citet{Konczak05} have proposed a way to compute possible and necessary winners when the knowledge of agent preferences is only partial, for various voting rules. They also showed that, even though this computation is hard in the general case, their method is polynomial in case of positional scoring rule. Later on, for the necessary winner problem, other authors have proposed polynomial-time algorithms when using maximin and Bucklin \citep{Xia2008}; sufficient conditions that ensure tractability have been proved \citep{Pini2007}.

@@

Although more interest has been shown in the incompleteness of agent preferences, several authors have considered scenarios where the voting rule is partially defined \citep{Stein1994}. Among others, \citet{Llamazares2013} have considered the problem of dealing with variable weights in positional scoring rules, and \citet{Walsh2007, Viappiani2018} consider the uncertainty in weights assuming a positional scoring rule has been considered under the assumption that the agents preferences are known. \commentOC{Check Walsh.}

Studies related to the manipulability of voting rules have been proposed in this context \citep{Endriss2016,Dey2018,Dey2018_2}, studying the reactions of agents when they learn incrementally about other agents preferences.

@@

\section{Empirical Evaluation} 
\label{sec:experiments}
\commentOC{
	\begin{enumerate}
		\item Pessimistic VS Elitist
		\item Reach regret: $n/10$. For this, we need $m^x n$ questions. (Correct formula)
		\item find a way of displaying the graph so that it is understandable in B/W.
		\item Check Pess VS XPess on other sizes.
		\item Prop qC in value of information
		\item Time comparison XPess VS Pess? (If time, check our estimate)
	\end{enumerate}
}
Our experiments are described by topic here below. We generally use the following protocol, deviations are indicated below for each experiment.

@@

We also see that Extended pessimistic performs slightly less well than Pessimistic. Although they come close, Extended pessimistic performs significatively less well, in the sense that the numbers are consistently in favor of Pessimistic if running the experiment again.

We next focus on the Pessimistic strategy, because Extended pessimistic is too slow to be ran repeatedly on much bigger problem sizes.

@@

\subsection{Value of information comparison}
\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{p} & {2 ph.\ ca} & {sd} & {2 ph.\ ag} & {sd} \\
			\midrule
			0 & 0.66 & 0.67 & 0.65 & 0.65  \\
			50 & 1.23 & 1.46 & 0.8 & 0.79 \\
			100 & 2.03 & 1.56 & 1.88 & 1.02  \\
			150 & 3.41 & 1.79 & 4.07 & 1.51 \\
			200 & 4.61	& 1.35  & 6.53 & 2.0  \\
			250 & 8.4 & 1.86 & 	7.69 & 1.24 \\
			300 &11.07 & 0.86& 11.87 & 1.25 \\
			350 &&&15.59 & 0.6 \\
			400 &20.0 & 0.0 & 20.0 & 20.0 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average $\MMR$ in problems of size $(10, 20)$ after $400$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair.}
	\label{tab:twoP400}
\end{table}

>>>>

\section{Related Work}
\label{sec:related}
In a social choice context, an increasing number of authors has been interested in obtaining information about winners with reduced assumptions about the knowledge of the agent preferences, assuming that the voting rule is known. \Citet{Conitzer2005} have studied the complexity of communication, using different voting rules, determining lower and upper bounds for it. They showed that, in the worst case, the agents should send their complete set of preference for most of the rules they investigated. \Citet{Konczak05} have proposed a way to compute possible and necessary winners when the knowledge of agent preferences is only partial, for various voting rules. They also showed that, even though this computation is hard in the general case, their method is polynomial in case of positional scoring rule. Later on, for the necessary winner problem, other authors have proposed polynomial-time algorithms when using maximin and Bucklin \citep{Xia2008}; showed that the general case remains computationally hard even when restricting to single-peaked preferences \citep{Walsh2007}; proved sufficient conditions that ensure tractability \citep{Pini2007}.

@@

Although more interest has been shown in the incompleteness of agent preferences, several authors have considered scenarios where the voting rule is partially defined. Among others, \citet{Llamazares2013} have considered the problem of dealing with variable weights in positional scoring rules, and \citet{Stein1994,Viappiani2018} consider the uncertainty in weights of a positional scoring rule assuming that the agents preferences are known.

Studies related to the manipulability of voting rules have been proposed in this context \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011}, and strategic behaviors, when agents learn incrementally about other agents preferences, have been investigated \citep{Endriss2016,Lev2019,Annemieke2012}.

@@

\section{Empirical Evaluation} 
\label{sec:experiments}
\commentOC{
	\begin{enumerate}
		\item Pessimistic VS Elitist Geometric
		\item Pessimistic VS Elitist VS Random
		\item 2 more lines in table
		\item Reach regret: $n/10$. For this, we need $m^x n$ questions. (Correct formula)
		\item find a way of displaying the graph so that it is understandable in B/W.
		\item Check Pess VS XPess on other sizes.
		\item Prop qC in value of information
		\item Time comparison XPess VS Pess? (If time, check our estimate)
	\end{enumerate}
}
Our experiments are described by topic here below. We generally use the following protocol, deviations are indicated below for each experiment.

@@

We also see that Extended pessimistic performs slightly less well than Pessimistic. Although they come close, Extended pessimistic performs significantly less well, in the sense that the numbers are consistently in favor of Pessimistic if running the experiment again.

We next focus on the Pessimistic strategy, because Extended pessimistic is too slow to be ran repeatedly on much bigger problem sizes.
\begin{table}
	\begin{center}
			\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
				\toprule
				{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {Eli.} & {sd} \\
				\midrule
				0 &20.0 & 0.0 & 20.0 & 0.0&  20.0 & 0.0 \\
				50 & 19.82 & 0.04 &	15.59 &0.56	&17.38& 0.7\\
				100 & 19.12	& 0.26&	11.91&	1.26 &15.23& 0.73\\
				150 & 18.06	& 0.47&	8.92&	1.53 &13.38& 1.11\\
				200 & 16.89	& 0.62&6.24&2.02&11.76& 1.03\\
				250 & 15.63 & 0.84&	4.64&1.72&10.56& 0.89\\
				300 & 14.72	& 0.94&	3.01& 1.35 &10.48& 0.87\\
				350 & 13.41	& 1.15& 1.76& 0.95&10.48& 0.86\\
				400 & 11.98	& 0.68&	0.62&0.56 &10.48& 0.86\\
				\bottomrule
			\end{tabular}
	\end{center}
	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions and $10$ runs.}
	\label{tab:biggerSize}
\end{table}

\begin{table}
	\begin{center}

			\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
				\toprule
				{sd} & {Pes.} & {sd} & {Eli.} & {sd} \\
				\midrule
				0	&20.0	&0.0	&20.0	&0.0\\
				50	&15.96	&0.54	&17.26	&0.42\\
				100	&12.48	&0.93	&15.6	&0.43\\
				150	&9.58	&1.37	&13.94	&0.76\\
				200	&7.43	&1.25	&10.95	&1.12\\
				250	&5.26	&1.52	&6.6	&0.79\\
				300	&3.47	&1.32	&6.57	&0.79\\
				350	&1.75	&1.36	&6.57	&0.79\\
				400	&0.49	&0.68	&6.57	&0.79\\
				\bottomrule
			\end{tabular}
	\end{center}
	\caption{Average MMR in problems of size $(10, 20)$ and geometric weights after $k$ questions and $10$ runs.}
	\label{tab:geometricWeights}
\end{table}

@@

\subsection{Value of information comparison}
\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{p} & {2 ph.\ ca} & {sd} & {2 ph.\ ac} & {sd} \\
			\midrule
			0 & 0.66 & 0.67 & 0.65 & 0.65  \\
			50 & 1.23 & 1.46 & 0.8 & 0.79 \\
			100 & 2.03 & 1.56 & 1.88 & 1.02  \\
			150 & 3.41 & 1.79 & 4.07 & 1.51 \\
			200 & 4.61	& 1.35  & 6.53 & 2.0  \\
			250 & 8.4 & 1.86 & 	7.69 & 1.24 \\
			300 &11.07 & 0.86& 11.87 & 1.25 \\
			350 &15.06 & 0.68&15.59 & 0.6 \\
			400 &20.0 & 0.0 & 20.0 & 20.0 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average $\MMR$ in problems of size $(10, 20)$ after $400$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair.}
	\label{tab:twoP400}
\end{table}
